Material Methods

### 2020-04-17 doc/MatMeth.Rmd
hopefully small changes

---
title: ''
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
  word_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_Main_Report.bib
---

>>>>

---
title: ''
date: '`r Sys.Date()`'
output:
  word_document:
    toc: yes
    toc_depth: '5'
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_Main_Report.bib
---
